A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-10-02 manuscript.Rmd
add link to latest release

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published," and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release, [zenodo.org](https://zenodo.org) or [figshare.com](https://figshare.com) can create a DOI, making it easier to reference and retrieve it (see the [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).

[^1]: To comment on our paper, please add an issue to the GitHub repository of our paper: [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).
[^doi]: [https://guides.github.com/activities/citable-code/](https://guides.github.com/activities/citable-code/)
[^sub]: We created an release for the submission: [https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.2.1-submission](https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.2.1-submission)

>>>>

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published,"[^pub] and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release, [zenodo.org](https://zenodo.org) or [figshare.com](https://figshare.com) can create a DOI, making it easier to reference and retrieve it (see the [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).

[^1]: To comment on our paper, please add an issue to the GitHub repository of our paper: [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).
[^doi]: [https://guides.github.com/activities/citable-code/](https://guides.github.com/activities/citable-code/)
[^sub]: We created an release for the submission: [https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.1.1-submission](https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.2.1-submission)
[^pub]: We created an release for the publication: [https://github.com/aaronpeikert/reproducible-research/releases/latest](https://github.com/aaronpeikert/reproducible-research/releases/latest)
